---
title: "Publications"
subtitle: "My research publications"
description: |
  My publications in paleoclimate science, automatically updated from Google Scholar.
date: "`r Sys.Date()`"
author: "Nick McKay"
draft: false
# layout options: single, single-sidebar
layout: single
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(scholar)
library(dplyr)
library(ggplot2)
library(DT)
library(knitr)
library(kableExtra)

# Nick McKay's Google Scholar ID
scholar_id <- "j8_CgoEAAAAJ"
```

This page automatically updates with publications from [Google Scholar](https://scholar.google.com/citations?user=j8_CgoEAAAAJ&hl=en) using the R `scholar` package.

---

## Publication Metrics

```{r metrics, results='asis'}
# Get citation data
profile <- get_profile(scholar_id)
citation_hist <- get_citation_history(scholar_id)

# Display key metrics
cat("**Total Citations:** ", profile$total_cites, "\n\n")
cat("**h-index:** ", profile$h_index, "\n\n") 
cat("**i10-index:** ", profile$i10_index, "\n\n")
cat("**Publications:** ", nrow(get_publications(scholar_id)), "\n\n")
```

---

## Citation History

```{r citation_plot, fig.cap="Citation history over time"}
# Plot citation history
ggplot(citation_hist, aes(x = year, y = cites)) +
  geom_col(fill = "steelblue", alpha = 0.7) +
  geom_smooth(method = "loess", se = FALSE, color = "darkred", size = 1.2) +
  labs(
    title = "Citations per Year",
    x = "Year",
    y = "Citations",
    caption = paste("Data retrieved:", Sys.Date())
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
```

---

## Recent Publications (Last 2 Years)

```{r recent_pubs}
# Filter for recent publications
recent_pubs <- pubs %>%
  filter(year >= (max(year, na.rm = TRUE) - 1)) %>%
  arrange(desc(year), desc(cites)) %>%
  mutate(
    formatted_citation = paste0(
      "<strong>", title, "</strong><br>",
      "<em>", author, "</em><br>",
      journal, " (", year, ")",
      ifelse(is.na(cites) | cites == 0, "", paste0("<br>Citations: ", cites))
    )
  )

# Display recent publications with blog post links
if(nrow(recent_pubs) > 0) {
  for(i in 1:min(10, nrow(recent_pubs))) {
    pub <- recent_pubs[i,]
    cat("### ", pub$year, "\n\n")
    cat(pub$formatted_citation, "\n\n")
    
    # Add blog post links for specific papers
    if(grepl("4.2 ka event is not remarkable", pub$title)) {
      cat("📖 **[Read the story behind this research](/blog/4.2ka-event-not-remarkable/)**\n\n")
    }
    if(grepl("Globally coherent water cycle response", pub$title)) {
      cat("📖 **[Read the story behind this research](/blog/global-water-cycle-response/)**\n\n")
    }
    if(grepl("global Data Assimilation of Moisture Patterns", pub$title)) {
      cat("📖 **[Read the story behind this research](/blog/damp21ka-data-assimilation/)**\n\n")
    }
    if(grepl("Arctic glacier snowline altitudes", pub$title)) {
      cat("📖 **[Read the story behind this research](/blog/arctic-snowline-rise/)**\n\n")
    }
    
    cat("---\n\n")
  }
} else {
  cat("No recent publications found.\n\n")
}
```

## Top Cited Publications

```{r top_cited}
# Get top cited publications
top_cited <- pubs %>%
  filter(!is.na(cites) & cites > 0) %>%
  arrange(desc(cites)) %>%
  head(10) %>%
  mutate(
    formatted_citation = paste0(
      "<strong>", title, "</strong><br>",
      "<em>", author, "</em><br>",
      journal, " (", year, ")<br>",
      "<strong>Citations: ", cites, "</strong>"
    )
  )

if(nrow(top_cited) > 0) {
  for(i in 1:nrow(top_cited)) {
    pub <- top_cited[i,]
    cat("**", i, ".** ", pub$formatted_citation, "\n\n")
    cat("---\n\n")
  }
} else {
  cat("Citation data not available.\n\n")
}
```

---

## Research Impact by Journal

```{r journal_analysis}
# Analyze publications by journal
journal_stats <- pubs %>%
  filter(!is.na(journal) & journal != "" & !is.na(cites)) %>%
  group_by(journal) %>%
  summarise(
    publications = n(),
    total_citations = sum(cites, na.rm = TRUE),
    avg_citations = round(mean(cites, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  filter(publications >= 2) %>%  # Only journals with 2+ publications
  arrange(desc(total_citations))

if(nrow(journal_stats) > 0) {
  journal_stats %>%
    head(15) %>%
    kable(format = "html", 
          col.names = c("Journal", "Publications", "Total Citations", "Avg Citations/Paper"),
          caption = "Publication and citation statistics by journal (minimum 2 publications)") %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE,
      font_size = 12
    )
} else {
  cat("Insufficient data for journal analysis.\n\n")
}
```

---

*This page is automatically generated from Google Scholar data and updates when the site is rebuilt. For the most current information, visit the [Google Scholar profile](https://scholar.google.com/citations?user=j8_CgoEAAAAJ&hl=en) directly.*

**Note:** Google Scholar data may occasionally be incomplete or delayed. If you notice any discrepancies, please [contact me](/contact/) to report them.