---
title: "Publications"
subtitle: "My research publications"
description: |
  My publications.
date: "`r Sys.Date()`"
author: "Nick McKay"
draft: false
# layout options: single, single-sidebar
layout: single
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(scholar)
library(dplyr)
library(ggplot2)
library(DT)
library(knitr)
library(kableExtra)

# Nick McKay's Google Scholar ID
scholar_id <- "j8_CgoEAAAAJ"
```


## Publication Metrics

```{r metrics, results='asis'}
# Get citation data
profile <- get_profile(scholar_id)
citation_hist <- get_citation_history(scholar_id)

# Get publications data (used throughout the document)
pubs <- get_publications(scholar_id)

# Display key metrics
cat("**Publications:** ", nrow(pubs), "\n\n")
cat("**Total Citations:** ", profile$total_cites, "\n\n")
cat("**h-index:** ", profile$h_index, "\n\n") 
cat("**i10-index:** ", profile$i10_index, "\n\n")
```

---

## Citation History

```{r citation_plot}
# Plot citation history
ggplot(citation_hist, aes(x = year, y = cites)) +
  geom_col(fill = "steelblue", alpha = 0.7) +
  #geom_smooth(method = "loess", se = FALSE, color = "darkred", size = 1.2) +
  labs(
    title = "Citations per Year",
    x = "Year",
    y = "Citations",
    caption = paste("Data retrieved:", Sys.Date())
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
```

---

## Publications from the last 2 years

```{r recent_pubs, results='asis'}
# Filter for recent publications
recent_pubs <- pubs %>%
  filter(year >= (max(year, na.rm = TRUE) - 1)) %>%
  arrange(desc(year), desc(cites))

# Display recent publications with blog post links
if(nrow(recent_pubs) > 0) {
  for(i in 1:min(10, nrow(recent_pubs))) {
    pub <- recent_pubs[i,]
    
    # Create Google Scholar search URL for the paper
    scholar_search_url <- paste0("https://scholar.google.com/scholar?q=", 
                                URLencode(paste(pub$title, pub$author), reserved = TRUE))
    
    cat("<strong><a href='", scholar_search_url, "' target='_blank'>", pub$title, "</a></strong>\n\n")
    cat("<em>", pub$author, "</em>\n\n")
    cat(pub$journal, " (", pub$year, ")")
    if(!is.na(pub$cites) && pub$cites > 0) {
      cat(" • Citations: ", pub$cites)
    }
    cat("\n\n")
    
    # Add blog post links for specific papers
    if(grepl("4.2 ka event is not remarkable", pub$title)) {
      cat("📖 **[Read my blog post about this research](/blog/4.2ka-event-not-remarkable/)**\n\n")
    }
    if(grepl("Globally coherent water cycle response", pub$title)) {
      cat("📖 **[Read my blog post about this research](/blog/global-water-cycle-response/)**\n\n")
    }
    if(grepl("global Data Assimilation of Moisture Patterns", pub$title)) {
      cat("📖 **[Read my blog post about this research](/blog/damp21ka-data-assimilation/)**\n\n")
    }
    if(grepl("Arctic glacier snowline altitudes", pub$title)) {
      cat("📖 **[Read my blog post about this research](/blog/arctic-snowline-rise/)**\n\n")
    }
    
    cat("---\n\n")
  }
} else {
  cat("No recent publications found.\n\n")
}
```

---

## Complete Publications List

```{r publications_table}
# Clean and format the data
pubs_formatted <- pubs %>%
  arrange(desc(year)) %>%
  mutate(
    # Create formatted citation
    citation = paste0(
      author, " (", year, "). ",
      "<strong>", title, "</strong>. ",
      "<em>", journal, "</em>",
      ifelse(is.na(number) | number == "", "", paste0(", ", number)),
      ifelse(is.na(cites) | cites == 0, "", paste0(" [Citations: ", cites, "]"))
    ),
    # Clean up journal names
    journal = ifelse(is.na(journal) | journal == "", "In Review/Preprint", journal)
  ) %>%
  select(Year = year, Citation = citation, Journal = journal, Citations = cites)

# Display as formatted table
pubs_formatted %>%
  select(Year, Citation, Citations) %>%
  kable(format = "html", escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = TRUE,
    font_size = 14
  ) %>%
  column_spec(1, width = "8%", bold = TRUE) %>%
  column_spec(2, width = "80%") %>%
  column_spec(3, width = "12%", bold = TRUE)
```

---

## Top Cited Publications

```{r top_cited, results='asis'}
# Get top cited publications
top_cited <- pubs %>%
  filter(!is.na(cites) & cites > 0) %>%
  arrange(desc(cites)) %>%
  head(10)

if(nrow(top_cited) > 0) {
  for(i in 1:nrow(top_cited)) {
    pub <- top_cited[i,]
    cat("<strong>", i, ".</strong> <strong>", pub$title, "</strong>\n\n")
    cat("<em>", pub$author, "</em>\n\n")
    cat(pub$journal, " (", pub$year, ") • <strong>Citations: ", pub$cites, "</strong>\n\n")
    cat("---\n\n")
  }
} else {
  cat("Citation data not available.\n\n")
}
```

---

## Research Impact by Journal

```{r journal_analysis}
# Analyze publications by journal
journal_stats <- pubs %>%
  filter(!is.na(journal) & journal != "" & !is.na(cites)) %>%
  group_by(journal) %>%
  summarise(
    publications = n(),
    total_citations = sum(cites, na.rm = TRUE),
    avg_citations = round(mean(cites, na.rm = TRUE), 1),
    .groups = 'drop'
  ) %>%
  filter(publications >= 2) %>%  # Only journals with 2+ publications
  arrange(desc(total_citations))

if(nrow(journal_stats) > 0) {
  journal_stats %>%
    head(15) %>%
    kable(format = "html", 
          col.names = c("Journal", "Publications", "Total Citations", "Avg Citations/Paper"),
) %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE,
      font_size = 12
    )
} else {
  cat("Insufficient data for journal analysis.\n\n")
}
```

---

*This page is automatically generated from Google Scholar data and updates when the site is rebuilt. For the most current information, visit the [Google Scholar profile](https://scholar.google.com/citations?user=j8_CgoEAAAAJ&hl=en) directly.*

**Note:** Google Scholar data may occasionally be incomplete or delayed. If you notice any discrepancies, please [contact me](/contact/) to report them.